R dyntrace report

### 2018-04-04 graphs/report-main.Rmd
Reporting etc.

pp <- function(number) format(number, big.mark=",", scientific=FALSE, trim=FALSE, digits=2)
load_local_csv <- function (csv_file) {
    path <- file.path(params$CSV_DIR, csv_file)
    write(paste("reading", path), stderr())
    as_tibble(read.csv(path, stringsAsFactors=FALSE))
}
print_data <- function (x) if(params$PRINT_DATA) print(x, row.names=FALSE)
prettify <- function(x) x %>% mutate(number=pp_trunc(number), percent=pp_perc(percent)) %>% as.data.frame
pp_trunc <- function(x) ifelse(x==0, paste(format(x, digits=2, scientific=FALSE)),
                               ifelse(x < 1000, format(x, digits=2, scientific=FALSE), 
                                      ifelse(x < 1000000, 
                                             paste(format(floor((x/1000)*10)/10, digits=2, scientific=FALSE), "k", sep=""), 
                                             paste(format(floor((x/1000000)*10)/10, digits=2, scientific=FALSE), "m", sep=""))))
pp_perc <- function(x) dollar_format(prefix="", suffix="%")(x)
is_outlier <- function(x) x < quantile(x, 0.25) - 1.5 * IQR(x) | x > quantile(x, 0.75) + 1.5 * IQR(x)

@@

<!--```{r child = 'report-basic-info.Rmd', params=params}				      
```-->

@@

>>>>

pp <- function(number) format(number, big.mark=",", scientific=FALSE, trim=FALSE, digits=2)
load_local_csv <- function (csv_file, backup=NULL) {
    path <- file.path(params$CSV_DIR, csv_file)
    write(paste("reading", path), stderr())
    tryCatch( 
      as_tibble(read.csv(path, stringsAsFactors=FALSE)),
      error=function(e) backup
    )
}
print_data <- function (x) if(params$PRINT_DATA) print(x, row.names=FALSE)
prettify <- function(x) x %>% mutate(number=pp_trunc(number), percent=pp_perc(percent)) %>% as.data.frame
pp_trunc <- function(x) ifelse(x==0, paste(format(x, digits=2, scientific=FALSE)),
                               ifelse(x < 1000, format(x, digits=2, scientific=FALSE), 
                                      ifelse(x < 1000000, 
                                             paste(format(floor((x/1000)*10)/10, digits=2, scientific=FALSE), "k", sep=""),
                                             ifelse(x < 1000000000,
                                                    paste(format(floor((x/1000000)*10)/10, digits=2, scientific=FALSE), "m", sep=""),
                                                    paste(format(floor((x/1000000000)*10)/10, digits=2, scientific=FALSE), "b", sep="")))))
pp_perc <- function(x) dollar_format(prefix="", suffix="%")(x)
is_outlier <- function(x) x < quantile(x, 0.25) - 1.5 * IQR(x) | x > quantile(x, 0.75) + 1.5 * IQR(x)

@@

```{r child = 'report-basic-info.Rmd', params=params}				      
```

@@

```{r child = 'report-what-do-specific-promises-return.Rmd', params=params}				      
```

```{r child = 'report-promise-forces-by-types.Rmd', params=params}				      
```

```{r child = 'report-promise-evaluation-distances.Rmd', params=params}				      
```

```{r child = 'report-interactions-among-promises.Rmd', params=params}				      
```

### 2018-04-04 graphs/report-number-of-accesses-to-a-promise.Rmd
Prints
Reporting etc.

``` {r, "number of accesses to a promise, aggregate", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
evaluations <- 
  load_local_csv("promise_evaluations.csv") #%>%
print(typeof(evaluations %>% pull(number)))
print(sum(as.numeric(evaluations %>% pull(number))))

evaluations <- evaluations %>% 
    group_by(no.of.evaluations) %>% 
    summarise(number=sum(as.numeric(number), na.rm=TRUE)) %>% 
    mutate(percent=100*number/sum(number)) %>%
    mutate(labels=no.of.evaluations) %>%
    mutate(no.of.evaluations=as.numeric(as.character(no.of.evaluations)))  %>%
    mutate(no.of.evaluations=ifelse(is.na(no.of.evaluations),
				     max(no.of.evaluations, na.rm=TRUE)+1, 
				                            no.of.evaluations)) %>% 
							    arrange(no.of.evaluations)

ggplot(evaluations, aes(x=no.of.evaluations, y=number)) + 
  geom_col() +
    scale_y_continuous(labels=pp_trunc) +
      scale_x_discrete(limit=0:11, labels=evaluations %>% pull(labels)) +
        theme(axis.title.x=element_blank(), legend.position="none") +
	  ylab("No. of promises") + xlab("No. of accesses")
	  ```

>>>>

``` {r, "number of accesses to a promise, aggregate", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
evaluations <- 
  load_local_csv("promise_evaluations.csv") %>%
  group_by(no.of.evaluations) %>% 
  summarise(number=sum(as.numeric(number), na.rm=TRUE)) %>% 
  mutate(percent=100*number/sum(number)) %>%
  mutate(labels=no.of.evaluations) %>%
  mutate(no.of.evaluations=as.numeric(as.character(no.of.evaluations)))  %>%
  mutate(no.of.evaluations=ifelse(is.na(no.of.evaluations),
                        	  	    max(no.of.evaluations, na.rm=TRUE)+1, 
				                          no.of.evaluations)) %>% 
	arrange(no.of.evaluations)

ggplot(evaluations, aes(x=no.of.evaluations, y=number)) + 
  geom_col() +
  scale_y_continuous(labels=pp_trunc) +
  scale_x_discrete(limit=0:11, labels=evaluations %>% pull(labels)) +
  theme(axis.title.x=element_blank(), legend.position="none") +
	ylab("No. of promises") + xlab("No. of accesses")

evaluations %>% select(labels, number, percent) %>% prettify %>% kable(col.names=c("no. of evaluations","number","percentage"), align="lrr")
```

### 2018-04-04 graphs/report-promise-code-types.Rmd
Prints
Reporting etc.

``` {r, "promise code types, aggregate", echo=FALSE, fig.width=10, fig.height=5}
promise_types <- 
  load_local_csv("promise_types.csv")

ggplot(promise_types %>% group_by(type) %>% summarise(number=sum(as.numeric(number))) %>% mutate(percent=100*number/sum(number)), 
       aes(x=type, y=number)) + 
  geom_col() +
  scale_y_continuous(labels=pp_trunc) +
  theme(axis.title.x=element_blank(), 
        legend.position="none", 
        axis.text.x=element_text(angle=90, vjust=.5)) +
  ylab("No. of promises") + 
  xlab("Promise type")
```

>>>>

``` {r, "promise code types, aggregate", echo=FALSE, fig.width=10, fig.height=5}
promise_types <- 
  load_local_csv("promise_types.csv") %>% 
  group_by(type) %>% summarise(number=sum(as.numeric(number))) %>% mutate(percent=100*number/sum(number))

ggplot(promise_types, aes(x=type, y=number)) + 
  geom_col() +
  scale_y_continuous(labels=pp_trunc) +
  theme(axis.title.x=element_blank(), 
        legend.position="none", 
        axis.text.x=element_text(angle=90, vjust=.5)) +
  ylab("No. of promises") + 
  xlab("Promise type")

promise_types %>% arrange(desc(number)) %>% prettify %>% kable(col.names=c("promise code type","number","percentage"), align="lrr")
```
